\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    {\Huge \scshape {Aiden Fan}} \\ \vspace{1pt}
    \href{mailto:aidenfan1648@gmail.com}{{aidenfan1648@gmail.com}} $|$
    \small 613-618-8379 $|$ 
    \href{https://linkedin.com/in/aiden-fan}{{Linkedin - Aiden Fan}} $|$
    \href{https://github.com/FanofAiden}{{Github - FanofAiden}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Carleton University}{Ottawa, ON}
      {Bachelor of Computer Science, Minor in Business $|$ 3rd Year $|$ CGPA: 10.2}{Expected May 2026}

  \resumeSubHeadingListEnd
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Relevant Courses}{: Data Structures and Algorithms (Java), Software Engineering (C++), Database Management Systems, Web Application Development, Systems Programming }
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Employment and Social Development Canada (ESDC)}{Gatineau, QC}
      {Software Developer/Programmer}{May 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Designed and deployed service applications for the Canadian Dental Care Plan's (CDCP) CRA assessment service, boosting robustness and performance.}
        \resumeItem{Developed REST API features using Apache Camel and Spring Boot in Java while using Maven as the primary testing tool, reducing bug reports and enhancing software reliability.}
        \resumeItem{In progress of enhancing department-wide back-end admin infrastructure, increasing admin control and flexibility within the program.}
        \resumeItem{Collaborated with development and operations teams to troubleshoot deployment/implementation issues, thereby cultivating cross-functional team cooperation and communication.}
        \resumeItem{Utilized Atlassian products (Jira, Confluence) and Azure DevOps for version control in a collaborative Agile Scrum team environment, ensuring quality and accuracy in meeting project timelines.}

      \resumeItemListEnd
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Mixtape Maker} $|$ \emph{iTunes Search API, SQLite, JavaScript, HTML/CSS, Node.js, Express.js,}}{}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application for users to create customized playlists of music.}
            \resumeItem{Implemented SQL to save and store user-specific playlists to the database, allowing for more functionality in the application.}
            \resumeItem{Used HTML/CSS for front-end aspects while leveraging Node.js and Express.js for robust back-end functionality.}
            \resumeItem{Integrated iTunes Search API with the back-end server, facilitating access to all possible songs released, enhancing user flexibility in playlist }
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Pokémon} $|$ \emph{Java, Swing (Java), JavaFX, Apache Netbeans}}{}
          \resumeItemListStart
            \resumeItem{Applied multi-threading to enable the random spawning of Pokémon while the user roams, increasing performance efficiency.}
            \resumeItem{Implemented a fighting function for battling other Pokémon, producing greater game capabilities.}
            \resumeItem{Engineered an interactive and intuitive GUI using Java Swing, thereby enhancing UX.}
          \resumeItemListEnd
    \resumeProjectHeading
          {\textbf{Phantom Hunt Simulation} $|$ \emph{C, Linux, Makefiles, Valgrind}}{}
          \resumeItemListStart
            \resumeItem{Improved throughput with multi-threading, allowing for ghost and hunter threads to function simultaneously.}
            \resumeItem{Developed multiple functionalities for the hunters and the ghost, resulting in a complete simulation.}
            \resumeItem{Utilized Valgrind to effectively debug while augmenting productivity to ensure a timely and accurate simulation.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Introduction to Cloud Computing} $|$ \href{https://www.coursera.org/account/accomplishments/certificate/WAG9BRR6M9MM}{{IBM}}}{June 2023}
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeProjectHeading
      {\textbf{DreamLaunch} $|$ \href{https://dreamlinked.ca/}{{DreamLinked}}}{July 2023}
      \resumeItemListStart
        \resumeItem{Participated in a 48-hour startup weekend where business ideas are brought to life and earned 3rd place.}
        \resumeItem{Collaborated with two team members to build a creative AI startup that utilizes AI agents in the workplace, improving productivity and business operations by 40\%.}
        \resumeItem{Successfully created and pitched the business model to founders and employees of startups.}
      \resumeItemListEnd
      \resumeItemListEnd
%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \begin{tabular}{ l l }
    \textbf{Languages:} & Java, Python, C/C++, JavaScript, C\#, SQL (Postgres)         \\
    \textbf{Technologies: } & RestAPI, HTML/CSS, Node.js, Express.js, PostgreSQL, SQLite, Excel \\
    \textbf{Frameworks: } & Apache Camel, Maven, Spring Boot, JavaFx, Swing \\
    \textbf{Development: } & Atlassian, Azure, Postman, SoapUI, Jira, Agile, Scrum, Linux, Git \\
\end{tabular}
\vspace{2mm}
 \end{itemize}


%-------------------------------------------
\end{document}
